---
title: "Wine Quality vs. Price"
author: "Scott Poese"
date: "August 7, 2018"
output: ioslides_presentation
---

```{r libraries, message=FALSE, echo=FALSE}
library(plotly)
library(ggplot2)
library(dplyr)
```

## Dataset Information

The plot here shows wine reviews from the dataset available from
https://www.kaggle.com/zynicide/wine-reviews/ and compares them to the price of
the wine.

```{r read, cache = TRUE}
wine <- read.csv("~/R/DevelopingDataProducts/wine-reviews/winemag-data-130k-v2.csv")
```

## Data Wrangling

The dataset is filtered to only show wines which had a price listed, and whose
price was not an outlier in the 1.5*IQR sense. Then 500 of these wines were
randomly selected to show a graph that was not too busy.

```{r filter}
wine <- wine[!is.na(wine$price),]
wine <- filter(wine,price < 1.5 * IQR(wine$price) + 
                       quantile(wine$price,.75))
set.seed(16)
wine <- wine[sample(nrow(wine),500),]
```

## Plot

The plot is then created using `ggplotly` (part of the `plotly' package).

```{r plot, message = FALSE}
p <- ggplot(data = wine, aes(x=price,y=points)) + 
        geom_point() + 
        geom_smooth() +
        labs(x = "Price(USD)", y = "Points", 
             title = "Wine Quality vs. Price")
gg <- ggplotly(p)
```

## Plot

```{r picture}
gg
```